Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-04 paper.tex

%Public transit schedules are made available on the Web in various ways, such as in a GTFS file, a route planning API, or through Linked Connections.
%This webservice provides an answer to a route planning question with parameters such as ``departuretime'', ``from'' and ``to''.
% Context & % Need
In the field of urban planning, researchers need an indication of how people move between cities. 
Yet, getting statistics of travel flows within public transit systems has proven to be troublesome.
% Task
We analyzed the query logs of the iRail API, a high expressive route planning API for the Belgian railways, to get an indication of travel flows between cities in Belgium.
We were able to study $\sim$100k to 500k requests for each month between October 2012 and November 2015, which is between $0.5\%$ and $1.7\%$ of the amount of monthly passengers.
% Object & Findings
Using data visualizations, we illustrated the commuting patterns in Belgium and show that Brussels, the capital, acts as a central hub. The Flemish region appears to be polycentric, while in the Walloon region, everything converges on Brussels.
The findings correspond to the real travel demand, say experts of the passenger federation Trein Tram Bus.
% Conclusion
We conclude that query logs of route planners are of high importance in getting an indication of the travel flows.
% Perspectives
High expressive transport data publishing methods such as route planning API exist, as well as low expressive data dumps or data fragments.
In order to be able to gather meaningful logs in all cases, we suggest using a separate POST request containing the entire query.

>>>>

%Public transit schedules are made available on the Web in various ways, such as in a GTFS file, a route planning API, or through Linked Connections.
%This webservice provides an answer to a route planning question with parameters such as ``departuretime'', ``from'' and ``to''.
% Context & % Need
In the field of urban planning, researchers need an indication of how people move between cities. 
Yet, getting statistics of travel flows within public transit systems has proven to be troublesome.
% Task
We analyzed the query logs of the iRail API, a high expressive route planning API for the Belgian railways, to get an indication of travel flows between cities in Belgium.
We were able to study $\sim$100k to 500k requests for each month between October 2012 and November 2015, which is between $0.5\%$ and $1.7\%$ of the amount of monthly passengers.
% Object & Findings
Using data visualizations, we illustrated the commuting patterns in Belgium and show that Brussels, the capital, acts as a central hub. The Flemish region appears to be polycentric, while in the Walloon region, everything converges on Brussels.
The findings correspond to the real travel demand, say experts of the passenger federation Trein Tram Bus.
% Conclusion
We conclude that query logs of route planners are of high importance in getting an indication of the travel flows.
% Perspectives
Nevertheless, we should be cautious about what we measure as GET requests on the Web are cacheable.
In order to have a query log for studying travel demand that works for all publishing strategies, we suggest future work to send anonymized POST requests from the end-user applications to an analytics server.
%High expressive transport data publishing methods such as route planning API exist, as well as low expressive data dumps or data fragments.
%In order to be able to gather meaningful logs in all cases, we suggest using a separate POST request containing the entire query.
